### 2025-09-17 paper/sec/authoring-workflow.tex
Simplify loopback description.

\begin{itemize}
    \item \textbf{Invalid Program}. Evaluation fails due a syntax error, undeclared identifer, division by
    zero, array index out of bounds or other runtime problem.
    \item \textbf{Invalid Output Type}.
    According to the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}), the expression is expected to return a string value.
    If the returned value is of a different type, an \textit{Invalid Output Type} error is raised.
    \item \textbf{Invalid Output Value}.
    The output produced by the generated expression is compared against the highlighted target text.
    If the values do not match, an \textit{Invalid Output Value} error is reported.
\end{itemize}

>>>>

\begin{itemize}
    \item \textbf{Invalid Program}. Evaluation fails due a syntax error, undeclared identifer, division by
    zero, array index out of bounds or other runtime problem.
    \item \textbf{Invalid Expression Type}. The value of the expression is not a string.
    \item \textbf{Mismatching String}. The value of the expression is a string, but is not equal to
    highlighted target text.
\end{itemize}
